Kids stove grades and usage summary

### 2020-01-27 home_char_act_summary.Rmd
Summary tables for abstacts/papers

---
title: "Kids home characteristics/activity summary"
author: "Ethan Walker"
date: "Started 15 Jan 2020, Updated 23 Jan 2020"
output:
  pdf_document: default
  word_document: default
---

@@

```{r}
# Load dataset
home_char_clean <- read_rds("Output/home_char_clean.rds")

home_act_clean <- read_rds("Output/home_act_clean.rds")
```

@@

>>>>

---
title: "Kids home characteristics/activity summary"
author: "Ethan Walker"
date: "Started 15 Jan 2020, Updated 27 Jan 2020"
output:
  pdf_document: default
  word_document: default
---

@@

```{r}
# Load dataset
home_char_clean <- read_rds("Output/home_char_clean.rds") 
home_act_clean <- read_rds("Output/home_act_clean.rds")
kids_linked_ids <- read_rds("Output/kids_linked_ids.rds")
pm_clean <- read_rds("Output/pm_clean.rds")
```

@@

#### Abstract/manuscript tables ####

# Filter for homes that have PM data
```{r}
# 93 Winter 1 placebo homes have PM data
pm_homes_placebo <- pm_clean %>% 
  filter(winter_id == 1) %>% 
  filter(treatment == "Placebo") %>% 
  group_by(area, home) %>% 
  mutate(initial_obs = if_else(pm_datetime_new == first_datetime_new, 1, 0)) %>% 
  filter(initial_obs == 1) %>% 
  mutate(pm_home = "true") %>% 
  select(area, home, home_winter_id, pm_home) %>% 
  ungroup() %>% 
  arrange(area, home)

home_char_filtered <- home_char_clean %>% 
  # change to correct joining data of interest
  left_join(pm_homes_placebo, by = c("area", "home", "home_winter_id")) %>% 
  filter(pm_home == "true") %>% 
  filter(winter_id == 1) %>% 
  ungroup() %>% 
  arrange(area, home)

home_act_filtered <- home_act_clean %>% 
  # change to correct joining data of interest
  left_join(pm_homes_placebo, by = c("area", "home", "home_winter_id")) %>% 
  filter(pm_home == "true") %>% 
  filter(winter_id == 1) %>% 
  ungroup() %>% 
  arrange(area, home)
```

# Summarize home data
```{r}
# Summarize numeric vars
kids_char <- home_char_filtered %>%  
  distinct(home, .keep_all = TRUE) %>%  
  group_by(area) %>% 
  summarize("Mean" = mean(home_furry, na.rm = TRUE), 
            "SD" = sd(home_furry, na.rm = TRUE),
            "min" = min(home_furry, na.rm = TRUE), 
            "max" = max(home_furry, na.rm = TRUE))
kable(kids_char, digits = 1, align = "c")

# Summarize factor vars
alaska_char <- home_act_filtered %>%  
  #distinct(home, .keep_all = TRUE) %>% 
  filter(area == "AK") %>% 
  group_by(home_act_sweep) %>% 
  #summarize(n = n(), percent = (n()/10)*100)
  summarize(n = n(), percent = (n()/60)*100)
alaska_char

navajo_char <- home_act_filtered %>%  
  #distinct(home, .keep_all = TRUE) %>% 
  filter(area == "NN") %>% 
  group_by(home_act_sweep) %>% 
  #summarize(n = n(), percent = (n()/23)*100)
  summarize(n = n(), percent = (n()/138)*100)
navajo_char

montana_char <- home_act_filtered %>%  
  #distinct(home, .keep_all = TRUE) %>% 
  filter(area == "WMT") %>% 
  group_by(home_act_sweep) %>% 
  #summarize(n = n(), percent = (n()/60)*100)
  summarize(n = n(), percent = (n()/360)*100)
montana_char

kids_char <- rbind(alaska_char, navajo_char, montana_char)
kids_char
```

### 2020-01-27 home_child_data_cleaning.Rmd
Summary tables for abstacts/papers

demographics_clean <- kids_demographics %>% 
  separate(intervention_time, c("trash", "intervention_time"), sep = " ") %>% 
  unite(intervention_datetime, c("intervention_date", "intervention_time"),
        sep = " ", remove = FALSE) %>% 
  mutate(intervention_datetime = ymd_hms(intervention_datetime)) %>% 
  select(-trash)

>>>>

demographics_clean <- kids_demographics %>% 
  separate(intervention_time, c("trash", "intervention_time"), sep = " ") %>% 
  unite(intervention_datetime, c("intervention_date", "intervention_time"),
        sep = " ", remove = FALSE) %>% 
  mutate(intervention_datetime = ymd_hms(intervention_datetime)) %>% 
  select(-trash) %>% 
  mutate(home_winter_id = as.numeric(home_winter_id),
         home_winter_id = if_else(home == "CH218" & winter_id == 1, 77, home_winter_id),
         home_winter_id = if_else(home == "CH218" & winter_id == 2, 111, home_winter_id),
         home_winter_id = as.factor(home_winter_id))

### 2020-01-27 indoor_temp_rh_summary.Rmd
Summary tables for abstacts/papers

---
title: "Kids indoor temp/RH summary"
author: "Ethan Walker"
date: "Started 15 Jan 2020, Updated 23 Jan 2020"
output: pdf_document
---

@@

```{r}
# Load data
indoor_temp_rh_clean <- read_rds("Output/indoor_temp_rh_clean.rds")
```

@@

>>>>

---
title: "Kids indoor temp/RH summary"
author: "Ethan Walker"
date: "Started 15 Jan 2020, Updated 27 Jan 2020"
output: pdf_document
---

@@

```{r}
# Load data
indoor_temp_rh_clean <- read_rds("Output/indoor_temp_rh_clean.rds")
kids_linked_ids <- read_rds("Output/kids_linked_ids.rds")
pm_clean <- read_rds("Output/pm_clean.rds")
```

@@

#### Abstract/manuscript tables ####

# Filter for homes that have PM data
```{r}
# 93 Winter 1 placebo homes have PM data
pm_homes_placebo <- pm_clean %>% 
  filter(winter_id == 1) %>% 
  filter(treatment == "Placebo") %>% 
  group_by(area, home) %>% 
  mutate(initial_obs = if_else(pm_datetime_new == first_datetime_new, 1, 0)) %>% 
  filter(initial_obs == 1) %>% 
  mutate(pm_home = "true") %>% 
  select(area, home, home_winter_id, pm_home) %>% 
  ungroup() %>% 
  arrange(area, home)

temp_rh_filtered <- indoor_temp_rh_clean %>% 
  # change to correct joining data of interest
  left_join(pm_homes_placebo, by = c("area", "home", "home_winter_id")) %>% 
  filter(pm_home == "true") %>% 
  filter(winter_id == 1) %>% 
  ungroup() %>% 
  arrange(area, home)
```

# Summarize home data
```{r}
# Summarize numeric vars
kids_temp_rh <- temp_rh_filtered %>%  
  distinct(home, .keep_all = TRUE) %>%  
  group_by(area) %>% 
  summarize("Mean" = mean(rh_indoor_min, na.rm = TRUE), 
            "SD" = sd(rh_indoor_min, na.rm = TRUE),
            "min" = min(rh_indoor_min, na.rm = TRUE), 
            "med" = median(rh_indoor_min, na.rm = TRUE), 
            "max" = max(rh_indoor_min, na.rm = TRUE))
kable(kids_temp_rh, digits = 1, align = "c")

```

### 2020-01-27 moisture_summary.Rmd
Summary tables for abstacts/papers

---
title: "Kids Moisture Summary"
author: "Ethan Walker"
date: "Started 22 Nov 2019, Updated 23 Jan 2020"
output: pdf_document
---

@@

```{r}
# Load data
moisture_clean <- read_rds("Output/moisture_clean.rds")
```

@@

>>>>

---
title: "Kids Moisture Summary"
author: "Ethan Walker"
date: "Started 22 Nov 2019, Updated 27 Jan 2020"
output: pdf_document
---

@@

```{r}
# Load data
moisture_clean <- read_rds("Output/moisture_clean.rds")
kids_linked_ids <- read_rds("Output/kids_linked_ids.rds")
pm_clean <- read_rds("Output/pm_clean.rds")
```

@@

#### Abstract/manuscript tables ####

# Filter for homes that have PM data
```{r}
# 93 Winter 1 placebo homes have PM data
pm_homes_placebo <- pm_clean %>% 
  filter(winter_id == 1) %>% 
  filter(treatment == "Placebo") %>% 
  group_by(area, home) %>% 
  mutate(initial_obs = if_else(pm_datetime_new == first_datetime_new, 1, 0)) %>% 
  filter(initial_obs == 1) %>% 
  mutate(pm_home = "true") %>% 
  select(area, home, home_winter_id, pm_home) %>% 
  ungroup() %>% 
  arrange(area, home)

moisture_filtered <- moisture_clean %>% 
  # change to correct joining data of interest
  left_join(pm_homes_placebo, by = c("area", "home", "home_winter_id")) %>% 
  filter(pm_home == "true") %>% 
  filter(winter_id == 1) %>% 
  ungroup() %>% 
  arrange(area, home)
```

# Summarize home data
```{r}
# Summarize numeric vars
kids_moisture <- moisture_filtered %>%  
  group_by(area) %>% 
  summarize("Mean" = mean(moisture_ave, na.rm = TRUE), 
            "SD" = sd(moisture_ave, na.rm = TRUE),
            "min" = min(moisture_ave, na.rm = TRUE), 
            "med" = median(moisture_ave, na.rm = TRUE), 
            "max" = max(moisture_ave, na.rm = TRUE))
kable(kids_moisture, digits = 1, align = "c")

table(moisture_filtered$area, moisture_filtered$moisture_split)
```

### 2020-01-27 pm_summary.Rmd
Summary tables for abstacts/papers

---
title: "Kids PM Summary"
author: "Ethan Walker"
date: "Started 22 Nov 2019, Updated 23 Jan 2020"
output: pdf_document
---

@@

# Summary stats
```{r}
pm_summary <- pm_clean %>% 
  # group by: area, treatment, dtid, day_of_week, Sampling_day
  filter(winter_id == 1 & treatment == "Placebo") %>% 
  filter(pm < 500) %>% 
  group_by(area) %>% 
  summarize("n" = n(),
            "Mean PM" = mean(pm, na.rm = TRUE), 
            "SD PM" = sd(pm, na.rm = TRUE),
            "Min PM" = min(pm, na.rm = TRUE), 
            "Median PM" = median(pm, na.rm = TRUE),
            "Max PM" = max(pm, na.rm = TRUE),
            "Mean Sample Days" = mean(pm_sample_interval, na.rm = TRUE),
            "Mean Sample Obs" = mean(pm_total_observations, na.rm = TRUE),
            "Mean % Daily Obs" = mean(percent_daily_obs_pm, na.rm = TRUE)) %>% 
  select(-area) %>% 
  t()

>>>>

---
title: "Kids PM Summary"
author: "Ethan Walker"
date: "Started 22 Nov 2019, Updated 27 Jan 2020"
output: pdf_document
---

@@

# Summary stats
```{r}
pm_summary <- pm_clean %>% 
  # group by: area, treatment, dtid, day_of_week, Sampling_day
  filter(winter_id == 1 & treatment == "Placebo") %>% 
  filter(pm < 500) %>% 
  group_by(area) %>% 
  summarize("n" = n(),
            "Mean PM" = mean(pm, na.rm = TRUE), 
            "SD PM" = sd(pm, na.rm = TRUE),
            "Min PM" = min(pm, na.rm = TRUE), 
            "25%" = quantile(pm, 0.25),
            "Median PM" = median(pm, na.rm = TRUE),
            "75%" = quantile(pm, 0.75),
            "Max PM" = max(pm, na.rm = TRUE),
            "Mean Sample Days" = mean(pm_sample_interval, na.rm = TRUE),
            "Mean Sample Obs" = mean(pm_total_observations, na.rm = TRUE),
            "Mean % Daily Obs" = mean(percent_daily_obs_pm, na.rm = TRUE)) %>% 
  select(-area) %>% 
  t()

### 2020-01-27 stove_grade_usage_summary.Rmd
Summary tables for abstacts/papers

---
title: "Kids stove grades and usage summary"
author: "Ethan Walker"
date: "Started 15 Jan 2020, Updated 23 Jan 2020"
output: pdf_document
---

@@

```{r}
# Load data
stove_grades_clean <- read_rds("Output/stove_grades_clean.rds")
stove_use_clean <- read_rds("Output/stove_use_clean.rds")
```

@@

>>>>

---
title: "Kids stove grades and usage summary"
author: "Ethan Walker"
date: "Started 15 Jan 2020, Updated 27 Jan 2020"
output: pdf_document
---

@@

```{r}
# Load data
stove_grades_clean <- read_rds("Output/stove_grades_clean.rds")
stove_use_clean <- read_rds("Output/stove_use_clean.rds")
kids_linked_ids <- read_rds("Output/kids_linked_ids.rds")
pm_clean <- read_rds("Output/pm_clean.rds")
```

@@

#### Abstract/manuscript tables ####

# Filter for homes that have PM data
```{r}
# 93 Winter 1 placebo homes have PM data
pm_homes_placebo <- pm_clean %>% 
  filter(winter_id == 1) %>% 
  filter(treatment == "Placebo") %>% 
  group_by(area, home) %>% 
  mutate(initial_obs = if_else(pm_datetime_new == first_datetime_new, 1, 0)) %>% 
  filter(initial_obs == 1) %>% 
  mutate(pm_home = "true") %>% 
  select(area, home, home_winter_id, pm_home) %>% 
  ungroup() %>% 
  arrange(area, home)

stove_use_filtered <- stove_use_clean %>% 
  # change to correct joining data of interest
  left_join(pm_homes_placebo, by = c("area", "home", "home_winter_id")) %>% 
  filter(pm_home == "true") %>% 
  filter(winter_id == 1) %>% 
  ungroup() %>% 
  arrange(area, home)

stove_grades_filtered <- stove_grades_clean %>% 
  # change to correct joining data of interest
  left_join(pm_homes_placebo, by = c("area", "home", "home_winter_id")) %>% 
  filter(pm_home == "true") %>% 
  filter(winter_id == 1) %>% 
  ungroup() %>% 
  arrange(area, home)
```

# Summarize home data
```{r}
# Summarize numeric vars
kids_use <- stove_use_filtered %>%  
  #distinct(home, .keep_all = TRUE) %>%  
  group_by(area) %>% 
  summarize("Mean" = mean(wood_cords, na.rm = TRUE), 
            "SD" = sd(wood_cords, na.rm = TRUE),
            "min" = min(wood_cords, na.rm = TRUE), 
            "med" = median(wood_cords, na.rm = TRUE), 
            "max" = max(wood_cords, na.rm = TRUE))
kable(kids_use, digits = 1, align = "c")

# Summarize factor vars
alaska_use <- stove_use_filtered %>%  
  #distinct(home, .keep_all = TRUE) %>% 
  filter(area == "AK") %>% 
  group_by(wood_collect_method) %>% 
  summarize(n = n(), percent = (n()/10)*100)
  #summarize(n = n(), percent = (n()/60)*100)
alaska_use

navajo_use <- stove_use_filtered %>%  
  #distinct(home, .keep_all = TRUE) %>% 
  filter(area == "NN") %>% 
  group_by(wood_collect_method) %>% 
  summarize(n = n(), percent = (n()/23)*100)
  #summarize(n = n(), percent = (n()/138)*100)
navajo_use

montana_use <- stove_use_filtered %>%  
  #distinct(home, .keep_all = TRUE) %>% 
  filter(area == "WMT") %>% 
  group_by(wood_collect_method) %>% 
  summarize(n = n(), percent = (n()/60)*100)
  #summarize(n = n(), percent = (n()/360)*100)
montana_use

kids_use <- rbind(alaska_use, navajo_use, montana_use)
kable(kids_use)

# stove grade table
stove_grades_filtered <- stove_grades_clean %>% 
  # change to correct joining data of interest
  left_join(pm_homes_placebo, by = c("area", "home", "home_winter_id")) %>% 
  arrange(area, home, winter_id) %>% 
  group_by(home) %>% 
  mutate(stove_grade = if_else(is.na(stove_grade), lead(stove_grade), stove_grade)) %>% 
  filter(pm_home == "true") %>% 
  filter(winter_id == 1) %>%
  filter(!is.na(stove_grade)) %>% 
  ungroup() %>% 
  arrange(area, home)

table(stove_grades_filtered$stove_grade, stove_grades_filtered$area)
```
